Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-02 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
primer añadido a related work

\section{Related Work}
\label{sec:related}
% C-IEAS
% Volunteer Based
% HBC
% Engagement Techniques
% Models

>>>>

\section{Related Work}
\label{sec:related}
% C-IEAS
Given the fatigue fitness evaluations produce in human users when applying IEAs, some authors have tried to mitigate the problem by allowing the algorithm to collaborate with the user, so that sometimes users perform the evaluation, but also specific measures are included into the algorithm to perform the evaluation of some features automatically.  For instance, Reis et al. added some terrain measures (such as accessibility and edge length) to a standard IEC in \cite{DBLP:journals/soco/FradeVC12} .  This way the algorithm was capable of providing terrains that would otherwise have need users evaluation for these specific features.

% Volunteer Based
% HBC
% Engagement Techniques
% Models
